Kelompok 4_Praktikum_Pekan 8

### 2024-04-08 Project/Kelompok 4_Praktikum_Pekan 8.Rmd
Update

```{r fig.height=3.5*3, fig.width=10*3, dpi=300}
plot_distribution <- function(data_awal, data_rataan, title, color) {
  df_awal <- data.frame(x = c(data_awal))
  df_rataan <- data.frame(x = data_rataan)

@@

@@

  plots <- plot_distribution(norm_samples[[which(sample_sizes == size)]], # Data Awal
                              norm_means[[which(sample_sizes == size)]], # Data Rataan
                              paste0("Distribusi Normal (n=", size, ")"), colors[1]) # Title & Colors
  plots_for_size <- c(plots_for_size, plots)

  plots <- plot_distribution(unif_samples[[which(sample_sizes == size)]], # Data Awal
                             unif_means[[which(sample_sizes == size)]], # Data Rataan
                             paste0("Distribusi Seragam (n=", size, ")"), colors[2]) # Title & Colors
  plots_for_size <- c(plots_for_size, plots)

  plots <- plot_distribution(exp_samples[[which(sample_sizes == size)]], # Data Awal
                             exp_means[[which(sample_sizes == size)]], # Data Rataan
                             paste0("Distribusi Eksponensial (n=", size, ")"), colors[3]) # Title & Colors
  plots_for_size <- c(plots_for_size, plots)

@@

>>>>

```{r fig.height=3.5*3, fig.width=10*3, dpi=300}
sample_size <- c(2, 5, 25)

plot_distribution <- function(data_awal, data_rataan, title, color) {
  df_awal <- data.frame(x = c(data_awal))
  df_rataan <- data.frame(x = data_rataan)

@@

for (size in sample_size) {
  plots_for_size <- list()

@@

  plots <- plot_distribution(norm_samples[[which(sample_size == size)]], # Data Awal
                              norm_means[[which(sample_size == size)]], # Data Rataan
                              paste0("Distribusi Normal (n=", size, ")"), colors[1]) # Title & Colors
  plots_for_size <- c(plots_for_size, plots)

  plots <- plot_distribution(unif_samples[[which(sample_size == size)]], # Data Awal
                             unif_means[[which(sample_size == size)]], # Data Rataan
                             paste0("Distribusi Seragam (n=", size, ")"), colors[2]) # Title & Colors
  plots_for_size <- c(plots_for_size, plots)

  plots <- plot_distribution(exp_samples[[which(sample_size == size)]], # Data Awal
                             exp_means[[which(sample_size == size)]], # Data Rataan
                             paste0("Distribusi Eksponensial (n=", size, ")"), colors[3]) # Title & Colors
  plots_for_size <- c(plots_for_size, plots)

@@

```{r fig.height=3.5*5, fig.width=10*5, dpi=300}
plot_distribution2 <- function(data_rataan, title, color) {
  df_rataan <- data.frame(x = data_rataan)

  return(list(p2, p3))
}

  plots <- plot_distribution2(norm_samples[[which(sample_sizes == size)]], # Data Awal
                              norm_means[[which(sample_sizes == size)]], # Data Rataan
                              paste0("Distribusi Normal (n=", size, ")"), colors[1]) # Title & Colors
  plots_for_size <- c(plots_for_size, plots)

  plots <- plot_distribution2(unif_samples[[which(sample_sizes == size)]], # Data Awal
                             unif_means[[which(sample_sizes == size)]], # Data Rataan
                             paste0("Distribusi Seragam (n=", size, ")"), colors[2]) # Title & Colors
  plots_for_size <- c(plots_for_size, plots)

  plots <- plot_distribution2(exp_samples[[which(sample_sizes == size)]], # Data Awal
                             exp_means[[which(sample_sizes == size)]], # Data Rataan
                             paste0("Distribusi Eksponensial (n=", size, ")"), colors[3]) # Title & Colors
  plots_for_size <- c(plots_for_size, plots)
